### 2016-03-24 paper.tex
Revise abstract to match the body

% Abstract: 150 words or less, extra 0.5in left and right margin.
% Note that all text is justified.
%
\begin{adjustwidth}{0.5in}{0.5in}
  \textbf{Abstract:}  \textit{Culture-narration games} are a promising
  genre for transformative games. This genre can be defined formal and
  dramatic characteristics, and we identify tabletop games that belong
  to the genre.  Adding technological components to the game affords
  new interaction modes as well as convenient digital distribution. We
  describe our team's pilot project at creating a technology-enhanced
  culture-narration game to improve cultural empathy among players aged
  10--14.  This pilot project highlights several complications with
  this genre, including thematic, technical, and production
  challenges.  However, the pilot project justifies continued
  experimentation, development, and formal assessment within the
  genre.
\end{adjustwidth}

>>>>

% Abstract: 150 words or less, extra 0.5in left and right margin.
% Note that all text is justified.
%
\begin{adjustwidth}{0.5in}{0.5in}
  \textbf{Abstract:} We are inspired by the educational potential of
  the board game \textit{Tales of the Arabian Nights}, which is a
  popular game among enthusiasts that teaches the player about the
  eponymous folk tale and the culture around it. Consider this game
  and others like it, we identify the characteristics that define a
  genre of \textit{culture-narration games}, which we consider to have
  untapped potential for educational and transformative games.
  We describe a design experiment through which a multidisciplinary team
  followed an iterative and incremental process, in collaboration
  with a community partner, to investigate the potential of this genre.
  The result is a game that uses a theme of monsters from around the
  world to teach cultural empathy.
  This pilot project reveals both the promise and the several complications
  with the genre, which lead to recommendations for future work.
\end{adjustwidth}
